### 2015-05-14 whoop.tex
space hack

\noindent\textbf{Architecture }
%
Figure~\ref{fig:whoop} depicts the \whoop toolchain. Initially, \whoop accepts a Linux driver written in C, together with an environmental model\footnote{This consists of stub header files modeling relevant Linux kernel APIs.} that is required to ``close'' the driver and allow it to be subsequently analyzed for data races. Both the driver and the Linux model are passed to the translation phase of \whoop (see Figure~\ref{fig:whoop} -- A), which uses three LLVM\footnote{\url{http://llvm.org}}-based tools, Chauffeur\footnote{\url{https://github.com/mc-imperial/chauffeur}}, Clang\footnote{\url{http://clang.llvm.org}} and SMACK\footnote{\url{https://github.com/smackers/smack}}~\cite{rakamaric2014smack}, to translate the original driver into an abstract program written in the Boogie intermediate verification language (IVL)~\cite{deline2005boogiepl}, a simple imperative language with well-defined semantics that is used as the input to a number of cutting-edge verifiers (e.g.\ Boogie and \corral).

Next, \whoop instruments and sequentializes the program to perform symbolic pairwise lockset analysis (see Figure~\ref{fig:whoop} -- B and \S\ref{sec:symbolicpairwise}) using the Boogie verification engine. After the verification phase ends, \whoop can exploit any inferred race-freedom guarantees to accelerate precise race-checking with \corral (see Figure~\ref{fig:whoop} -- C and \S\ref{corral}).

>>>>

\noindent\textbf{Architecture }
%
Figure~\ref{fig:whoop} depicts the \whoop toolchain. The input to \whoop is a Linux driver written in C, together with an environmental model\footnote{This consists of stub header files modeling relevant Linux kernel APIs.} that is required to ``close'' the driver so that it can be analyzed for races. Initially, \whoop uses three LLVM\footnote{\url{http://llvm.org}}-based tools, Chauffeur\footnote{\url{https://github.com/mc-imperial/chauffeur}}, Clang\footnote{\url{http://clang.llvm.org}} and SMACK\footnote{\url{https://github.com/smackers/smack}}~\cite{rakamaric2014smack}, to translate the driver and its environmental model into an abstract program written in the Boogie intermediate verification language (IVL)~\cite{deline2005boogiepl}, a simple imperative language with well-defined semantics that is used as the input to a number of cutting-edge verifiers (e.g.\ Boogie and \corral). Next, \whoop instruments and sequentializes the program to perform symbolic pairwise lockset analysis (see Figure~\ref{fig:whoop} -- B and \S\ref{sec:symbolicpairwise}) using the Boogie verification engine. After the verification phase ends, \whoop can exploit any inferred race-freedom guarantees to accelerate precise race-checking with \corral (see Figure~\ref{fig:whoop} -- C and \S\ref{corral}).
